---
title: "Massachusetts COVID-19 Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
---

This page displays analysis of Massachusetts COVID-19 data from the Massachusetts Department of Public Health (MDPH) and the Massachusetts Wastewater Resources Authority (MWRA). 
<br>
<br>

```{r, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE}
deploy <- TRUE

if(deploy == FALSE){
  setwd("/Users/conorkelly/Documents/ckelly17.github.io")
}
source("mass.R")
```

## Daily statistics from MDPH
The charts below display daily data compiled by MDPH on COVID-19 cases, hospitalizations, and deaths in Massachusetts. The most recent data is through ``r max_date_mass``.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(mass_case_plot, width = 800)
ggplotly(ma_log, width = 800)
ggplotly(mass_ratio, width = 800)
ggplotly(ma_test_plt, width = 800)

```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(mass_hosps_plt, width = 800)

```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(mass_deaths_plot, width = 800)
ggplotly(mass_cfr_plot, width = 800)

```
## Wastewater Analysis
```{r, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE}
if(deploy == FALSE){
  setwd("/Users/conorkelly/Documents/ckelly17.github.io")
}
source("ma_wastewater.R")

```
The charts below display data collected by the Massachusetts Wastewater Resources Authority (MWRA) on levels of COVID-19 in Boston-area wastewater. For more information, see the [MWRA site](https://www.mwra.com/biobot/biobotdata.htm). 

Last MWRA update: ``r updated``

```{r, echo=FALSE, warning=FALSE, message=FALSE}
fig
log_fig
ratio
```

**Sources**

*COVID-19 Response Reporting*. Massachusetts Department of Public Health. https://www.mass.gov/info-details/covid-19-response-reporting

*Wastewater COVID-19 Tracking*. Massachusetts Water Resources Authority. https://www.mwra.com/biobot/biobotdata.htm

Last checked: ``r last_checked``