---
title: "Examples of my work"
output:
  html_document:
    toc: true
    toc_float: true
---
Below are examples of my data analysis work from over the last year: 


## Hanover Research
While I can't publish the products of my work at Hanover, here are a few examples of projects completed in the last year:

* Equity Audit Dashboard for PGCPS
* District performance benchmarking
* Early warning system for Grade 9


## COVID-19
I've been focused on COVID-19 data since the beginning of the pandemic. 

My main project has been maintaining a dashboard that uses daily data from The COVID Tracking Project (public API) and the New York Times (GitHub repo). To date, it has been viewed over 150,000 times on my Tableau public page.

### Visualization
### Code
### Writing


```{r , echo=FALSE}
plot(pressure)
```

### R code
### Dashboard
### Articles and publications

## 2020 Election
```{r , echo=FALSE}
plot(pressure)
```

### R code
```{r , echo=FALSE}
plot(pressure)
```

### Polling Dashboard



```{r , echo=FALSE}
plot(pressure)
```
### COVID Tracking Project
```{r , echo=FALSE}
plot(pressure)
```

### Polling Analysis
```{r , echo=FALSE}
plot(pressure)
```