---
title: "South Africa COVID Update"
output: 
  html_document:
    toc: true
    toc_float: true
---

Cases, deaths, and testing data provided by [Our World in Data](https://ourworldindata.org/) on [GitHub](https://github.com/owid/covid-19-data/tree/master/public/data) via [Johns Hopkins](https://github.com/CSSEGISandData/COVID-19) and [South Africa Department of Health](https://sacoronavirus.co.za/). Hospitalization data from the Data Science for Social Impact Research Group @ University of Pretoria, *Coronavirus COVID-19 (2019-nCoV) Data Repository for South Africa*. Available on: https://github.com/dsfsi/covid19za.

I display data since the beginning of 2021. My processing and analysis code can be found [here](https://github.com/ckelly17/South-Africa-COVID-19). Many thanks to all who have made this data available.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("/Users/conorkelly/Documents/COVID/south africa.R")
```
## Cases

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(sa_case_plot)
ggplotly(sa_ratio_log)

```

The line chart below shows the weekly growth multiplier of seven-day average cases. Values over 100% indicate case growth, while values under 100% mean case decline. For example, a 200% growth multiplier would mean cases are twice as high as the week before (rising); 50% would mean that they are only half as high (falling). Dots show daily values compared to seven days earlier. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}

ggplotly(sa_ratio_plot)
```

## Deaths

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(sa_deaths_plot)
ggplotly(sa_deaths_log)
```

**Percentage of peak values**
This charts display the 7-day average for deaths (black) and cases (orange) over time, expressed as the percentage of the all-time high values reached in summer 2021. Deaths are lagged by 17 days, the observed gap between the peak of cases and the peak of deaths during the summer of 2021 (Delta wave). It is designed to explore differences in disease severity over time.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(pct_pk_plot) %>%
  layout(legend = list(orientation = "h", x =0.25, y = .97))
```

**Case fatality rate**
This chart displays the 7-day average for deaths (lagged 17 days) divided by the 7-day average for cases. The lag reflects the observed gap between the peak of cases and the peak of deaths during the summer of 2021 (Delta wave). The chart includes a `loess` smoothing. 


```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(cfr_plot)
```

## Test Positivity 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(pos_rate_plot)

```
## Hospitals
Data from Data Science for Social Impact Research Group @ University of Pretoria via [GitHub](https://github.com/dsfsi/covid19za/blob/master/data/covid19za_provincial_raw_hospitalization.csv). Presented first for South Africa as a whole and then for Gauteng Province specifically. Dashed lines indicate the date (Nov 25, 2021) when the Omicron variant was announced by the South Africa National Institute for Communicable Diseases.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(sa_hosp)
```

**Gauteng Province**

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(gt_hosp)
```

**Percentage of Peak Values** 
Case and hospitalization metrics (seven-day averages) over time as percentage of peak values. No lags are applied. The gray area chart shows the progression of cases over time, while the lines show hospitalization metrics.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplotly(pct_hosp_plot) %>%
  layout(legend = list(orientation = "h", x =0.15, y = 1.05))

ggplotly(icu_pct_plot) %>%
  layout(legend = list(orientation = "h", x =.62, y = .92))
```


## Data Table (JHU)

```{r warning=FALSE, message=FALSE, echo=FALSE}
library(lubridate)
library(pracma)
library(data.table)

cases <- as_tibble(fread("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")) %>%
  mutate(var = "cases")

deaths <- as_tibble(fread("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")) %>%
  mutate(var = "deaths")

cases %>%
  bind_rows(deaths) %>%
  select(-Lat, -Long) %>%
  pivot_longer(cols = -c(`Province/State`, `Country/Region`, var),
               names_to = 'date',
               values_to = 'total') %>%
  filter(`Country/Region` %in% "South Africa") %>%
  select(-c(`Province/State`, `Country/Region`)) %>%
  mutate(date = mdy(date)) %>%
  mutate(weekday = wday(date, label = TRUE, abbr = FALSE)) %>%
  arrange(date) %>%
  group_by(var) %>%
  mutate(new = total - lag(total)) %>%
  mutate(avg_7day = movavg(new, 7)) %>%
  tail(16) %>%
  arrange(var) %>%
  knitr::kable(align = 'c')
  
```

